Ecological performance of detecting data fabrication with summary statistics

### 2017-03-08 submission/manuscript.Rnw
Update the ML3 data file, based on Charlie's emails from October 2016.

<<data prepper, echo=FALSE,results=hide>>=
# Dynamically generate path names
ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/ML3StroopRaw.csv', x12)
ml3_clean_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/StroopCleanSet.csv', x12)
pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)

>>>>

<<data prepper, echo=FALSE,results=hide>>=
# Dynamically generate path names
ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/StroopCleanSet.csv', x12)
pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
